Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-07 submission.tex
tabell-fiksing

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Training} & \textbf{Testing} & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        Gold & Gold & 90.15\% & 92.51\% \\
        Gold & Auto & 85.68\% & 88.98\% \\
        Auto & Auto & 87.01\% & 90.19\% \\
        \bottomrule
    \end{tabular}
    \caption{Results of parsing with Mate using various configurations of PoS
      tag sources in training and testing: \emph{Gold} denotes gold standard
      tags and \emph{Auto} denotes tags automatically predicted by TnT.}
    \label{tagconfigeval}
\end{table}

@@

The hope is that the introduction of more fine-grained linguistically motivated
distinctions in the tag set may assist the parser in recognizing and
generalizing syntactic patterns.  However, this would also increase the
complexity of the tagging task, which can be expected to lead to a drop in
tagger accuracy.  The best tagging, evaluated in isolation, does not
necessarily lead to the best parse, hence the aim of this section is to
investigate how tag set modifications affect this interplay.

@@

\subsection{Baseline Experiments}
In an initial round of experiments, we concatenated the tag of each token with
its full set of morphological features, thereby mapping the original tag set to a
new maximally fine-grained tag set, given the annotations available in the
treebank. This resulted in a total of 368 tags,
hereafter referred to as the \emph{full} tag set.
The two initial tag sets, i.e., the original tag set comprising 19 tags and the
full tag set comprising 368 tags, thus represent two extremes in terms of
granularity.
To establish some initial points of reference for how tag set granularity affects the
performance of tagging and parsing on NDT, we trained and tested a full pipeline with both of
these initial tags sets. The results are reported in Table \ref{inittagseteval}.
Unsurprisingly, we see that the tagger accuracy
plummets when we move from the original to the full tag set. While the MFT
tagging baseline for the original tag set is 94.14\%, it drops by almost 9
percentage points to 85.15\% for the full tag set. TnT yields
97.47\% accuracy on the original tag set, which drops to 93.48\% for the full tag
set. These results confirm our hypothesis that the high level linguistic
information
in the full, fine-grained tag set comes at the expense of reduced tagger
performance.  In spite of this, however, we see that the additional information
in the full tag set still improves the parser performance. With the original tag set, Mate
achieves 87.01\% LAS and 90.19\% UAS, which for the full tag set increases to 87.15\% and
90.39\%, respectively. These
preliminary results are encouraging in indicating that the additional linguistic
information assists syntactic parser, motivating further optimization of the
tag set.

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}lllll@{}}
        \toprule
        \textbf{Tag Set} & \textbf{MFT} & \textbf{Acc} &
        \textbf{LAS} & \textbf{UAS} \\
        \midrule
        Original & \textbf{94.14\%} & \textbf{97.47\%} & 87.01\% & 90.19\% \\
        Full & 85.15\% & 93.48\% & \textbf{87.15\%} & \textbf{90.39\%} \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing our development section of NDT with
        the two initial tag sets. From left to right, we report the tagger
        accuracy of the most-frequent-tag baseline, the tagger accuracy of TnT,
        and the labeled attachment score and the unlabeled attachment score for
        the Mate parser.}
    \label{inittagseteval}
\end{table}

@@

\begin{table}
    \centering
    \smaller[1]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS}
        \\
        \midrule
        --- & 97.47\% & 87.01\% & 90.19\% \\
        Case & \textbf{97.48\%} & 87.63\% & 90.72\% \\
        Definiteness & 97.00\% & 88.27\% & 91.42\% \\
        Gender & 96.09\% & 87.21\% & 90.36\% \\
        Number & 96.37\% & 87.97\% & 91.00\% \\
        Type & 96.92\% & 88.07\% & 91.11\% \\
        Case \& definiteness & 97.03\% & 88.39\% & 91.44\% \\
        Type \& case & 96.92\% & 88.46\% & 91.51\% \\
        Type \& definiteness & 96.99\% & 88.44\% & 91.48\% \\
        %Type \& number & 96.37\% & 87.95\% & 90.95\% \\
        Type, case \& definiteness & 97.05\% & \textbf{88.81\%} &
        \textbf{91.73\%} \\
        %Type, definiteness \& number & 96.46\% & 88.06\% & 91.12\% \\
        \bottomrule
    \end{tabular}
    \caption{Tagging and parsing with modified PoS tags for nouns. The first
      row corresponds to using the original tag set unmodified.}
    \label{substresults}
\end{table}

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        --- & \textbf{97.47\%} & 87.01\% & 90.19\% \\
        Mood & 97.43\% & 87.04\% & 90.19\% \\
        Tense & 97.30\% & 86.97\% & 90.18\% \\
        Voice & 97.45\% & 86.96\% & 90.09\% \\
        Mood \& tense & 97.31\% & 87.12\% & 90.31\% \\
        Voice \& tense & 97.28\% & 86.99\% & 90.15\% \\
        Mood, tense \& voice & 97.27\% & 86.83\% & 90.05\% \\
        Finiteness & 97.35\% & \textbf{87.30\%} & \textbf{90.43\%} \\
        \bottomrule
    \end{tabular}
    \caption{Tagging and parsing with modified PoS tags for verbs.}
    \label{verbresults}
\end{table}

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS}
        \\
        \midrule
        --- & \textbf{97.47\%} & 87.01\% & 90.19\% \\
        Definiteness & 96.84\% & 87.14\% & 90.29\% \\
        Degree & 97.41\% & \textbf{87.29\%} & \textbf{90.44\%} \\
        Gender & 96.89\% & 87.10\% & 90.25\% \\
        Number & 96.71\% & 86.99\% & 90.10\% \\
        Type & 97.40\% & 87.11\% & 90.25\% \\
        Definiteness \& degree & 96.81\% & 87.23\% & 90.39\% \\
        Definiteness \& gender & 96.31\% & 87.18\% & 90.39\% \\
        Definiteness \& number & 96.78\% & 87.27\% & \textbf{90.44\%} \\
        %Degree \& gender & 96.87\% & 87.00\% & 90.16\% \\
        %Degree \& number & 96.76\% & 87.13\% & 90.26\% \\
        %Definiteness, degree \& number & 96.81\% & 87.14\% & 90.30\% \\
        \bottomrule
    \end{tabular}
    \caption{Tagging and parsing with modified PoS tags for adjectives.}
    \label{adjresults}
\end{table}

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        --- & 97.47\% & 87.01\% & 90.19\% \\
        Definiteness & 97.49\% & \textbf{87.30\%} & \textbf{90.42\%} \\
        Gender & 97.28\% & 87.09\% & 90.31\% \\
        Number & 97.49\% & 87.04\% & 90.18\% \\
        Type & \textbf{97.61\%} & 87.00\% & 90.11\% \\
        \bottomrule
    \end{tabular}
    \caption{Tagging and parsing with modified PoS tags for determiners.}
    \label{detresults}
\end{table}

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        --- & 97.47\% & 87.01\% & 90.19\% \\
        Case & 97.50\% & 87.08\% & 90.21\% \\
        Gender & 97.48\% & 87.06\% & 90.23\% \\
        Number & 97.49\% & 87.21\% & 90.33\% \\
        Person & 97.49\% & 87.22\% & 90.32\% \\
        Type & 97.48\% & 87.19\% & 90.40\% \\
        Number \& person & 97.49\% & 96.98\% & 90.16\% \\
        Type \& case & 97.51\% & \textbf{87.30\%} & \textbf{90.41\%} \\
        Type \& number & 97.49\% & 87.27\% & \textbf{90.41\%} \\
        Type \& person & 97.49\% & 87.00\% & 90.14\% \\
        Type, case \& number & \textbf{97.52\%} & 87.11\% & 90.36\% \\
        \bottomrule
    \end{tabular}
    \caption{Tagging and parsing with modified PoS tags for pronouns.}
    \label{pronresults}
\end{table}

\subsection{Optimized Tag Set}
\begin{table*}[ht]
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llllll@{}}
        \toprule
        \textbf{Category} & \textbf{Feature(s)} & \textbf{MFT} &
        \textbf{Acc} & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        \emph{Original} & --- & 94.14\% & 97.47\% & 87.01\% & 90.19\% \\
        Noun & Type, case \& definiteness & 89.61\% & 97.05\% & 88.81\% &
        91.73\% \\
        Verb & Finiteness & 93.72\% & 97.35\% & 87.30\% & 90.43\% \\
        Adjective & Degree & 94.13\% & 97.41\% & 87.29\% & 90.44\% \\
        Determiner & Definiteness & 94.13\% & 97.49\% & 87.30\% & 90.42\% \\
        Pronoun & Type \& case & 94.12\% & 97.51\% & 87.30\% & 90.41\% \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing with the most successful tag set
        modification for each category.}
    \label{respectiveresults}
\end{table*}

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Tag} & \textbf{Description} \\
        \midrule
        \texttt{adj|komp} & Comparative adjective \\
        \texttt{adj|pos} & Positive adjective \\
        \texttt{adj|sup} & Superlative adjective \\
        \texttt{det|be} & Definite determiner \\
        \texttt{det|ub} & Indefinite determiner \\
        \texttt{pron|pers} & Personal pronoun \\
        \texttt{pron|pers|akk} & Personal pronoun, accusative \\
        \texttt{pron|pers|nom} & Personal pronoun, nominative \\
        \texttt{pron|refl} & Reflexive pronoun \\
        \texttt{pron|res} & Reciprocal pronoun \\
        \texttt{pron|sp} & Interrogative pronoun \\
        \texttt{subst|appell} & Common noun \\
        \texttt{subst|appell|be} & Common noun, def. \\
        \texttt{subst|appell|be|gen} & Common noun, def., genitive \\
        \texttt{subst|appell|ub} & Common noun, indef. \\
        \texttt{subst|appell|ub|gen} & Common noun, indef., genitive \\
        \texttt{subst|prop} & Proper noun \\
        \texttt{subst|prop|gen} & Proper noun, genitive \\
        \texttt{verb|fin} & Finite verb \\
        \texttt{verb|infin} & Nonfinite verb \\
        \bottomrule
    \end{tabular}
    \caption{Overview of the optimized tag set.}
    \label{optimizedtagset}
\end{table}

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llllll@{}}
        \toprule
        \textbf{Data} & \textbf{Tag Set} & \textbf{MFT} & \textbf{Acc} &
        \textbf{LAS} & \textbf{UAS} \\
        \midrule
        \multirow{2}{*}{Dev}
        & Original & \textbf{94.14\%} & \textbf{97.47\%} & 87.01\% & 90.19\% \\
        %Full & 85.15\% & 93.48\% & 87.15\% & 90.39\% \\
        & Optimized & 85.15\% & 96.85\% & \textbf{88.87\%} & \textbf{91.78\%} \\
        \midrule
        \multirow{2}{*}{Test}
        & Original & \textbf{94.22\%} & \textbf{97.30\%} & 86.64\% & 90.07\% \\
        %& Full & 84.27\% & 92.79\% & 87.03\% & 90.16\% \\
        & Optimized & 88.08\% & 96.35\% & \textbf{88.55\%} & \textbf{91.41\%} \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing with the optimized tag set,
        compared to the original NDT coarse tag set. The parser is both trained and tested using
        automatically predicted tags from TnT.}
    \label{finalresults}
\end{table}

>>>>

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Training} & \textbf{Testing} & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        Gold & Gold & 90.15 & 92.51 \\
        Gold & Auto & 85.68 & 88.98 \\
        Auto & Auto & 87.01 & 90.19 \\
        \bottomrule
    \end{tabular}
    \caption{Results of parsing with Mate using various configurations of PoS
      tag sources in training and testing: \emph{Gold} denotes gold standard
      tags and \emph{Auto} denotes tags automatically predicted by TnT.}
    \label{tagconfigeval}
\end{table}

@@

The hope is that the introduction of more fine-grained linguistically motivated
distinctions in the tag set may assist the parser in recognizing and
generalizing syntactic patterns.  This would also increase the
complexity of the tagging task though, which can be expected to lead to a drop in
tagger accuracy. However, the best tagging, evaluated in isolation, does not
necessarily lead to the best parse, hence the aim of this section is to
investigate how tag set modifications affect this interplay.

@@

\subsection{Baseline Experiments}
In an initial round of experiments, we concatenated the tag of each token with
its full set of morphological features, thereby mapping the original tag set to a
new maximally fine-grained tag set, given the annotations available in the
treebank. This resulted in a total of 368 tags,
hereafter referred to as the \emph{full} tag set.
The two initial tag sets, i.e., the original tag set comprising 19 tags and the
full tag set comprising 368 tags, thus represent two extremes in terms of
granularity.
To establish some initial points of reference for how tag set granularity affects the
performance of tagging and parsing on NDT, we trained and tested a full pipeline with both of
these initial tags sets. The results are reported in Table \ref{inittagseteval}.
Unsurprisingly, we see that the tagger accuracy
plummets when we move from the original to the full tag set. While the MFT
tagging baseline for the original tag set is 94.14\%, it drops by almost 9
percentage points to 85.15\% for the full tag set. TnT yields
97.47\% accuracy on the original tag set, which drops to 93.48\% for the full tag
set. These results confirm our hypothesis that the high level of linguistic
information
in the full, fine-grained tag set comes at the expense of reduced tagger
performance.  In spite of this, however, we see that the additional information
in the full tag set still improves the parser performance. With the original tag set, Mate
achieves 87.01\% LAS and 90.19\% UAS, which for the full tag set increases to 87.15\% and
90.39\%, respectively. These
preliminary results are encouraging in indicating that the additional linguistic
information assists syntactic parser, motivating further optimization of the
tag set.

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}lllll@{}}
        \toprule
        \textbf{Tag Set} & \textbf{MFT} & \textbf{Acc} &
        \textbf{LAS} & \textbf{UAS} \\
        \midrule
        Original & \textbf{94.14} & \textbf{97.47} & 87.01 & 90.19 \\
        Full & 85.15 & 93.48 & \textbf{87.15} & \textbf{90.39} \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing our development section of NDT with
        the two initial tag sets. From left to right, we report the tagger
        accuracy of the most-frequent-tag baseline, the tagger accuracy of TnT,
        and the labeled attachment score and the unlabeled attachment score for
        the Mate parser.}
    \label{inittagseteval}
\end{table}

@@

\begin{table}
    \centering
    \smaller[1]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS}
        \\
        \midrule
        --- & 97.47 & 87.01 & 90.19 \\
        Case & \textbf{97.48} & 87.63 & 90.72 \\
        Definiteness & 97.00 & 88.27 & 91.42 \\
        Gender & 96.09 & 87.21 & 90.36 \\
        Number & 96.37 & 87.97 & 91.00 \\
        Type & 96.92 & 88.07 & 91.11 \\
        Case \& definiteness & 97.03 & 88.39 & 91.44 \\
        Type \& case & 96.92 & 88.46 & 91.51 \\
        Type \& definiteness & 96.99 & 88.44 & 91.48 \\
        %Type \& number & 96.37 & 87.95 & 90.95 \\
        Type, case \& definiteness & 97.05 & \textbf{88.81} &
        \textbf{91.73} \\
        %Type, definiteness \& number & 96.46 & 88.06 & 91.12 \\
        \bottomrule
    \end{tabular}
    \caption{Tagging and parsing with modified PoS tags for nouns. The first
      row corresponds to using the original tag set unmodified.}
    \label{substresults}
\end{table}

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        --- & \textbf{97.47} & 87.01 & 90.19 \\
        Mood & 97.43 & 87.04 & 90.19 \\
        Tense & 97.30 & 86.97 & 90.18 \\
        Voice & 97.45 & 86.96 & 90.09 \\
        Mood \& tense & 97.31 & 87.12 & 90.31 \\
        Voice \& tense & 97.28 & 86.99 & 90.15 \\
        Mood, tense \& voice & 97.27 & 86.83 & 90.05 \\
        Finiteness & 97.35 & \textbf{87.30} & \textbf{90.43} \\
        \bottomrule
    \end{tabular}
    \caption{Tagging and parsing with modified PoS tags for verbs.}
    \label{verbresults}
\end{table}

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS}
        \\
        \midrule
        --- & \textbf{97.47} & 87.01 & 90.19 \\
        Definiteness & 96.84 & 87.14 & 90.29 \\
        Degree & 97.41 & \textbf{87.29} & \textbf{90.44} \\
        Gender & 96.89 & 87.10 & 90.25 \\
        Number & 96.71 & 86.99 & 90.10 \\
        Type & 97.40 & 87.11 & 90.25 \\
        Definiteness \& degree & 96.81 & 87.23 & 90.39 \\
        Definiteness \& gender & 96.31 & 87.18 & 90.39 \\
        Definiteness \& number & 96.78 & 87.27 & \textbf{90.44} \\
        %Degree \& gender & 96.87 & 87.00 & 90.16 \\
        %Degree \& number & 96.76 & 87.13 & 90.26 \\
        %Definiteness, degree \& number & 96.81 & 87.14 & 90.30 \\
        \bottomrule
    \end{tabular}
    \caption{Tagging and parsing with modified PoS tags for adjectives.}
    \label{adjresults}
\end{table}

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        --- & 97.47 & 87.01 & 90.19 \\
        Definiteness & 97.49 & \textbf{87.30} & \textbf{90.42} \\
        Gender & 97.28 & 87.09 & 90.31 \\
        Number & 97.49 & 87.04 & 90.18 \\
        Type & \textbf{97.61} & 87.00 & 90.11 \\
        \bottomrule
    \end{tabular}
    \caption{Tagging and parsing with modified PoS tags for determiners.}
    \label{detresults}
\end{table}

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llll@{}}
        \toprule
        \textbf{Feature(s)} & \textbf{Acc} & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        --- & 97.47 & 87.01 & 90.19 \\
        Case & 97.50 & 87.08 & 90.21 \\
        Gender & 97.48 & 87.06 & 90.23 \\
        Number & 97.49 & 87.21 & 90.33 \\
        Person & 97.49 & 87.22 & 90.32 \\
        Type & 97.48 & 87.19 & 90.40 \\
        Number \& person & 97.49 & 96.98 & 90.16 \\
        Type \& case & 97.51 & \textbf{87.30} & \textbf{90.41} \\
        Type \& number & 97.49 & 87.27 & \textbf{90.41} \\
        Type \& person & 97.49 & 87.00 & 90.14 \\
        Type, case \& number & \textbf{97.52} & 87.11 & 90.36 \\
        \bottomrule
    \end{tabular}
    \caption{Tagging and parsing with modified PoS tags for pronouns.}
    \label{pronresults}
\end{table}

\subsection{Optimized Tag Set}
\begin{table*}[ht]
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llllll@{}}
        \toprule
        \textbf{Category} & \textbf{Feature(s)} & \textbf{MFT} &
        \textbf{Acc} & \textbf{LAS} & \textbf{UAS} \\
        \midrule
        \emph{Original} & --- & 94.14 & 97.47 & 87.01 & 90.19 \\
        Noun & Type, case \& definiteness & 89.61 & 97.05 & 88.81 &
        91.73 \\
        Verb & Finiteness & 93.72 & 97.35 & 87.30 & 90.43 \\
        Adjective & Degree & 94.13 & 97.41 & 87.29 & 90.44 \\
        Determiner & Definiteness & 94.13 & 97.49 & 87.30 & 90.42 \\
        Pronoun & Type \& case & 94.12 & 97.51 & 87.30 & 90.41 \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing with the most successful tag set
        modification for each category.}
    \label{respectiveresults}
\end{table*}

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}ll@{}}
        \toprule
        \textbf{Tag} & \textbf{Description} \\
        \midrule
        \texttt{adj|komp} & Comparative adjective \\
        \texttt{adj|pos} & Positive adjective \\
        \texttt{adj|sup} & Superlative adjective \\
        \texttt{det|be} & Definite determiner \\
        \texttt{det|ub} & Indefinite determiner \\
        \texttt{pron|pers} & Personal pronoun \\
        \texttt{pron|pers|akk} & Personal pron., accusative \\
        \texttt{pron|pers|nom} & Personal pron., nominative \\
        \texttt{pron|refl} & Reflexive pronoun \\
        \texttt{pron|res} & Reciprocal pronoun \\
        \texttt{pron|sp} & Interrogative pronoun \\
        \texttt{subst|appell} & Common noun \\
        \texttt{subst|appell|be} & Common noun, def. \\
        \texttt{subst|appell|be|gen} & Common noun, def., genitive \\
        \texttt{subst|appell|ub} & Common noun, indef. \\
        \texttt{subst|appell|ub|gen} & Common noun, indef., gen. \\
        \texttt{subst|prop} & Proper noun \\
        \texttt{subst|prop|gen} & Proper noun, genitive \\
        \texttt{verb|fin} & Finite verb \\
        \texttt{verb|infin} & Nonfinite verb \\
        \bottomrule
    \end{tabular}
    \caption{Overview of the optimized tag set.}
    \label{optimizedtagset}
\end{table}

@@

\begin{table}
    \centering
    \smaller[0.5]
    \begin{tabular}{@{}llllll@{}}
        \toprule
        \textbf{Data} & \textbf{Tag Set} & \textbf{MFT} & \textbf{Acc} &
        \textbf{LAS} & \textbf{UAS} \\
        \midrule
        \multirow{2}{*}{Dev}
        & Original & \textbf{94.14} & \textbf{97.47} & 87.01 & 90.19 \\
        %Full & 85.15\% & 93.48\% & 87.15\% & 90.39\% \\
        & Optimized & 85.15 & 96.85 & \textbf{88.87} & \textbf{91.78} \\
        \midrule
        \multirow{2}{*}{Test}
        & Original & \textbf{94.22} & \textbf{97.30} & 86.64 & 90.07 \\
        %& Full & 84.27\% & 92.79\% & 87.03\% & 90.16 \\
        & Optimized & 88.08 & 96.35 & \textbf{88.55} & \textbf{91.41} \\
        \bottomrule
    \end{tabular}
    \caption{Results of tagging and parsing with the optimized tag set,
        compared to the original NDT coarse tag set. The parser is both trained and tested using
        automatically predicted tags from TnT.}
    \label{finalresults}
\end{table}
